Asteroseismology of GD358 with complex C/O core profiles

### 2016-08-15 msnew.tex
Added a paragraph about convection zone influence on modes (Mike's poster) updated noise figure, changed 2015 to 2016, fixed a few typos

\author {Agn\`es~Bischoff-Kim\altaffilmark{1},
J.~L. Provencal\altaffilmark{2,3},
M.~H.~Montgomery\altaffilmark{3,4},
Samuel~T.~Harrold\altaffilmark{4},
B.~Howard\altaffilmark{3},
W.~Strickland\altaffilmark{5},
D.~Chandler\altaffilmark{5},
D.~Campbell\altaffilmark{5},
A.~Arredondo\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~P.~Russell\altaffilmark{5},
D.~Doyle\altaffilmark{5},
A.~Brickhouse\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~Peters\altaffilmark{5},
A.~V.~Kusakin\altaffilmark{6},
A.~V.~Sergeev\altaffilmark{7},
M.~Andreev\altaffilmark{7},
A.~Maksim\altaffilmark{7},
S. Velichko\altaffilmark{7}
R.~Janulis\altaffilmark{8},
F.~Ali\c cavu\c s\altaffilmark{9},
N. Horoz\altaffilmark{9},
S.~Zola\altaffilmark{10,11},
W.~Og{\l}oza\altaffilmark{10,11},
D.~Koziel-Wierzbowska{10,11},
T.~Kundera\altaffilmark{10,11},
D. Jableka\altaffilmark{10,11},
B. Debski\altaffilmark{10,11},
S. Meingast\altaffilmark{12}
}
\altaffiltext{1}{Penn State Worthington Scranton, Dunmore, PA 18512; axk55@psu.edu}
\altaffiltext{2}{University of Delaware, Department of Physics and Astronomy
Newark, DE 19716; jlp@udel.edu}
\altaffiltext{3}{Delaware Asteroseismic Research Center, Mt. Cuba Observatory,
Greenville, DE 19807}
\altaffiltext{4}{Department of Astronomy, University of Texas, Austin, TX 78712;
mikemon@rocky.as.utexas.edu}
\altaffiltext{5}{Meyer Observatory and Central Texas Astronomical Society, 209
Paintbrush, Waco, TX 76705; chandler@vvm.com}
\altaffiltext{6}{Fesenkov Astrophysical Institute, Almaty 050020, Kazakhstan}
\altaffiltext{7}{Ukrainian National Academy of Sciences, Main Astronomical
Observatory, Golosiiv, Kiev 022 252650; sergeev@terskol.com }
\altaffiltext{8}{Institute of Theoretical Physics and Astronomy, Vilnius
University, Vilnius, Lithuania; jr@itpa.lt}
\altaffiltext{9}{Ulupinar Observatory, \c Canakkale Onsekiz Mart University, Turkey}
\altaffiltext{10}{Astronomical Observatory of the Jagiellonian University, ul. Orla
171, 30-244 Cracow, Poland; szola@oa.uj.edu.pl}
\altaffiltext{11}{Mount Suhora Observatory, Cracow Pedagogical University, Ul.
Podchorazych 2, 30-084 Krakow, Poland; zola@astro1.as.ap.krakow.pl}
\altaffiltext{12}{Institut f\H ur Astrophysik, Universit\H at Wien, T\H urkenschanzstrasse 17, 1180 Wien, Austria}

@@

\begin{abstract}
We report on the analysis of 33 years of photometric observations of the pulsating
helium atmosphere white dwarf GD358.  The complete data set includes archival data from 1982-2006, 
and 1105.1 hours of new observations from 2007-2015. From this data set, we extract 15 frequencies 
representing g-mode pulsation modes, adding 4 modes to the 11 modes 
known previously. We present evidence that these 15 modes are $\ell=1$ modes, 13 of which belong to 
a consecutive sequence in radial overtone
$k$. We perform a detailed asteroseismic analysis using models that include parameterized, complex carbon and oxygen 
core composition profiles to fit the periods. Recent spectroscopic analyses place GD358 near the red edge of the DBV instability strip, at 24,000 $\pm$ 500~K and a \logg of 7.8 $\pm$ 0.08 dex. The surface gravity translates to a mass range of 0.455 to 0.540 \msun. Our best fit model has a temperature of 23,650~K and a mass of 0.5706 \msun ~. That is slightly more massive than what the most recent spectroscopy suggests. We find a pure helium layer mass of $10^{-5.50}$, consistent with the outward diffusion of helium over time.

@@

The subject of this paper, GD358 (V777 Her) is the brightest ($m_{\rm v}=13.7$) and best 
studied helium atmosphere white dwarf pulsator. It is located near the red edge of the 
instability strip, with a spectroscopic temperature of \teff\ $=24000\pm500$ ~K and \logg\ $=7.8$ 
\citep{Koester2013}. GD358's pulsation spectrum contains a series of independent 
radial overtones, many with complex frequency structure.  For one epoch of data taken during a WET run, models involving magnetic fields and oblique rotation have been proposed to explain such structure \citep{Montgomery10}.

@@

GD358 was discovered in 1982 \citep{Winget82} and has been the target of the Whole 
Earth Telescope (WET) in 1990, 1994, 2000, and 2006 \citep{Provencal09, Kepler03,Winget94}. 
New observations presented here include 254 individual observing runs (1105.1 hrs) spanning 
2007-2015 (Table \ref{journal}). Each season of observations was obtained as part of 
multisite WET campaigns \citep{wet90}.

@@

\begin{figure}
\epsscale{0.7}
\plotone{terskol}
\caption{Light curve of GD358 obtained with the Peak Terskol 2.0 m telescope.  Each point corresponds 
to a 10 s exposure. The nonlinear, multiperiodic nature of this star is clearly evident.
(A color version of this figure is available in the online journal.)
\label{tersk}
}
\end{figure}

The complexities associated with GD358's pulsations (see Section \ref{freq}) led us to also 
re-reduce all available archival data \citep{Provencal09, Kepler03, Winget94, Winget82} 
insure continuity in methodology. The final result is a series of light curves 
for each observing season between 1982 and 2015. 
For the new observations, 2007 contains 8.1 hrs of observation, 2008 26.1 hrs, 2009 45 hrs, 
2010 201.3 hrs, 2011 401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, and 2015 55 hrs. 
Our coverage is not complete, and this incompleteness produces spectral leakage in the 
amplitude spectra. To quantify this, we sampled single sinusoids using exactly the 
same times as the original data for each season. The resulting amplitude spectrum, 
or ``spectral window'', is the pattern produced in the FT by a single frequency. 
The FTs for 2010, 2011, and 2014 are given in Fig.~\ref{fts}.

@@

We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
select statistically significant peaks in each FT. We adopt the criterion that a peak must have 
an amplitude at least four times greater than the average noise level in the given frequency range 
\citep{Provencal12}. We define ``noise'' as the frequency-dependent 
average amplitude after removal of the dominant frequencies. This is a conservative estimate, 
as it is impossible to ensure that all of the ``real'' frequencies are removed when determining
the noise level. This is certainly true for GD358, where the peaks above $\approx$ 2500 $\mu$Hz\ 
are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
as a function of frequency for the 2007-2015 observing seasons. A similar plot for the 
archival data is presented in Fig. 3 of \citet{Provencal09}. To confirm our uncertainty 
estimates, we calculated Monte Carlo simulations using the routine provided in {\sl Period04}.  
This routine generates a set of light curves using the original times, the fitted frequencies and 
amplitudes, and added Gaussian noise. A least squares fit is performed on each simulated light 
curve, with the distribution of fit parameters giving the uncertainties. Our Monte Carlo results 
are consistent with our average noise estimates.

\begin{figure}
\plotone{noise}
\caption{A comparison of the average noise as a function of frequency for the 2007-2015 observing 
seasons.  Each data set was prewhitened by its dominant frequencies.  The noise levels for each 
season are somewhat different.  This must be taken into account during frequency analysis.  
\label{noise}
}
\end{figure}

Having established our baseline noise levels, we proceed to frequency selection and identification.
Our frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
fitting a sinusoid at that frequency to the data set, subtracting the fit from the light curve, 
recomputing the FT, examining the residuals, and repeating the process until no significant power 
remains. This technique, known as prewhitening, must be employed with an over-abundance of caution, 
especially since we are aware of amplitude and/or frequency modulation in our data set. A detailed
discussion of the prewhitening procedure and steps taken to minimize the effects of amplitude 
modulation is given in \citep{Provencal09}. Our final identifications of independent frequencies
detected in each observing season are given in Table \ref{freq1} and Table \ref{freq2}.

@@

\subsection{Frequencies Distribution}

Perusal of Tables \ref{freq1} and \ref{freq2} shows that GD358's observed frequencies vary in two
important ways.  First, frequencies detected in a given observing season are not found 
in all observing seasons. Asteroseismology is based on the assumption that the available pulsation
frequencies are linked to stellar structure.  Since we are fairly certain that GD358's internal structure 
does not change on the timescales of the observations, we can assume that GD358 excites 
different subsets of its available pulsations at different times. While this is a common phenomenon
seen in white dwarf pulsators, the selection mechanism remains unknown. The best way to 
determine GD358's complete set of pulsation frequencies is to combine frequency identifications 
from multiple observing seasons as outlined in \citet{Kleinman98}.

\begin{figure}
\epsscale{0.8}
%\plottwo{gd358multif_2015.eps}{gd358multi.eps}
%\centering{
%\includegraphics[width=1.0]{gd358multif_2015.eps}
%}
\plotone{gd358multif_2015.eps}
\caption{A schematic representation of GD358's pulsation modes for all available data between
1982 and 2015. Systematic patterns of distribution are evident. The bands between 2400 and 1000
\muHz\ (400 and 1000 s) are of particular importance for this work. (A color version of this 
figure is available in the online journal.)
\label{schematic}
}
\end{figure}

Fig.~\ref{schematic} presents a schematic representation of GD358's 
independent frequencies detected between 1982 and 2015.  
The features of asteroseismic importance are the localized bands between 900 and 2400
\muHz\ (1100 and 400 s). We interpret the bands to represent a series of radial overtone $k$. The bands
themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
frequency detections from multiple observing seasons, but each band is significantly wider in 
frequency space than the frequency error of any single measurement, arguing that some process 
is acting on the frequencies. The simplest explanation is rotational splitting.  However, with the 
exception of the two highest frequency (shortest period) bands ($k=8$ and $k=9$ 
from \citet{Provencal09}), we find no clear evidence of multiplet structure in the frequency 
distributions of the lower frequency (longer period) bands (Fig.~\ref{rot}). The lower frequency band widths are 
most likely the result of some process producing amplitude and/or frequency modulation that obscures 
any underlying signatures of rotational splitting.

\begin{figure}
 \epsscale{1.0}
 \plotone{gd358k17_k8.eps}
% \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
 \caption{The detailed schematic distribution of frequencies for the bands near 1300({\em{right}}
 and 2360 \muHz\ ({\em{left}}). As an example of the higher frequency bands, the 1300 \muHz\ band 
 shows no multiplet structure, unlike the 2360 \muHz\ band. Here we see clear evidence of multiplet 
 structure. Assuming the triplet represents
 $\ell=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the x scale for both axes.
 (A color version of this figure is available in the online journal.)
 \label{rot}}
\end{figure}

Fig. \ref{schematic} also shows that the widths of the bands are not constant, but change 
from band to band. \citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator 
(DAV) KIC4552982, in which they identify 17 bands of pulsation frequencies. KIC4552982 is one of the 
coolest ZZ Cetis known \citep{Tremblay2013}, and it follows the general pattern exhibited 
by GD358: the highest frequency (shortest period) mode shows evidence of rotational splitting, while the 
lower frequency (longer period) modes are complex bands. The authors note that this DAV's bands have 
different widths in frequency space, and that there may be astronomical significance to this. 
Although the observational timebases and coverage are quite different (20 continuous months 
for KIC4552982 vs 33 incomplete years for GD358), our data presents the opportunity to investigate this 
for a cooler DB pulsator.  We measured the widths of each of GD358's band where we have
more than 10 detections. We define ''width'' as the difference between the lowest and highest frequency 
detected in each band. Fig. \ref{thick} presents the results. We find no correlation of width with number
of detected peaks in each band. Interestingly, the widths of GD358's bands are commensurate with those 
found in KIC4552982. We find a general increase in width with decreasing frequency (increasing period), 
until we reach the band at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.

A second interesting behavior is given by the distribution of average amplitudes for the bands 
(Fig~\ref{schematic}. In particular, the two bands at 1857.7 and 2007.6  \muHz\ have never been observed 
at amplitudes above 4 mma. The band at 1369 \muHz\ is also only observed at lower amplitudes. Interestingly, 
the band at 1741.5 \muHz\ was not observed at large amplitude prior to 2006, and it has remained at high 
amplitude since that time.

In broad brush strokes, the observed global pulsations involve the whole star, but each pulsation samples the star
in slightly different ways.  For example, modes with lower frequencies (higher radial $k$ values) preferentially 
sample the outer layers, while modes with higher frequencies (lower radial $k$ values) have outer turning points 
that are farther from the surface, and so sample the deeper interior. It makes intuitive sense that lower 
frequency modes would be affected by processes confined to the outer stellar atmosphere. We speculate that the 
observed band widths and pulsation amplitudes contain information about the convection zone and/or any surface
magnetic field. Further investigation requires guidance from theory.

@@

\subsection{Mode Identification}\label{mode}
Our current work has produced a well defined sequence of modes, adding to 
previous studies \citep{Montgomery10, Provencal09, Metcalfe00, Winget94}. The previous 
identification of these modes as a series of $l$=1 radial overtones is based mostly on 
the pulsation frequency distribution and limited spectroscopic analysis 
\citep{Kotak02, Castanheira05}. It is important to further investigate these identifications 
as we initiate an indepth asteroseismic investigation.

@@

Finally, given the $l$=1 identification and the lack of definite multiplet structure for the higher 
frequency modes, the best way to determine the central frequency for each band is simply to 
average the detected frequencies in the bands.  We experimented with numerous weighting techniques, 
and determined there is no significant difference in our solutions.  Our final frequencies for each band 
are given in Table~\ref{gd}. We use these periods in our asteroseismic fitting.

@@

To compute our models, we used the White Dwarf Evolution Code (WDEC). The WDEC uses hot  and self-consistently allows them to relax to be solutions of the equations of stellar structure with the temperature of our choice.
polytrope models with temperatures above 100{,}000~K as starting model and numericaly evolves them until they are thermally relaxed 
solutions to the stellar structure equations and have the temperature of our choice. The mass is also fixed as an input, and so is the internal chemical composition profiles (no mass loss, no time dependent diffusion of elements). Each model we compute for our grids is the result 
of such an evolutionary sequence. The WDEC is described in detail in \citet{Lamb75} and 
\citet{Wood90}. We used smoother core composition profiles and implemented more complex profiles 
that result from stellar evolution calculations \citep{Salaris97}. We updated the envelope 
equation of state tables from those calculated by \citet{Fontaine77} to those given by 
\citet{Saumon95}. We use OPAL opacities \citep{Iglesias96} and plasmon neutrino rates 
published by \citet{Itoh96}.

@@

Before we refine the period-by-period fitting optimization, it is worthwhile to step back and consider 
what we can learn from the average period spacing of GD358. The average period spacing provides an 
asteroseismic measure of the mass and temperature of the star, independent of the details of 
internal chemical composition profiles. Higher $k$ modes are not strongly trapped in the core and 
according to asymptotic theory, they should be nearly evenly spaced in period. This spacing is 
given by (Unno et al. 1989)

>>>>

\author {Agn\`es~Bischoff-Kim\altaffilmark{1},
J.~L. Provencal\altaffilmark{2,3},
M.~H.~Montgomery\altaffilmark{3,4},
H.~L. Shipman\altaffilmark{2,3},
Samuel~T.~Harrold\altaffilmark{4},
B.~Howard\altaffilmark{3},
W.~Strickland\altaffilmark{5},
D.~Chandler\altaffilmark{5},
D.~Campbell\altaffilmark{5},
A.~Arredondo\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~P.~Russell\altaffilmark{5},
D.~Doyle\altaffilmark{5},
A.~Brickhouse\altaffilmark{5},
R.~Linn\altaffilmark{5},
D.~Peters\altaffilmark{5},
P.~A. Bradley\altaffilmark{6},
S.-L. Kim\altaffilmark{7},
X.~J.~Jiang\altaffilmark{8},
Y-N.~Mao\altaffilmark{8},
A.~V.~Kusakin\altaffilmark{9},
A.~V.~Sergeev\altaffilmark{10,11},
M.~Andreev\altaffilmark{10,11},
A.~Maksim\altaffilmark{10,11},
S. Velichko\altaffilmark{12},
R.~Janulis\altaffilmark{12},
E.~Pakstiene\altaffilmark{12},
F.~Ali\c cavu\c s\altaffilmark{13},
N. Horoz\altaffilmark{13},
S.~Zola\altaffilmark{14,15},
W.~Og{\l}oza\altaffilmark{14,15},
D.~Koziel-Wierzbowska\altaffilmark{14,15},
T.~Kundera\altaffilmark{14,15},
D. Jableka\altaffilmark{14,15},
B. Debski\altaffilmark{14,15},
S. Meingast\altaffilmark{16},
T. Nagel\altaffilmark{17},
L. Loebling\altaffilmark{17},
C. Heinitz\altaffilmark{17},
D. Hoyer\altaffilmark{17},
Zs. Bogn\'ar\altaffilmark{18}
}
\altaffiltext{1}{Penn State Worthington Scranton, Dunmore, PA 18512; axk55@psu.edu}
\altaffiltext{2}{University of Delaware, Department of Physics and Astronomy
Newark, DE 19716; jlp@udel.edu}
\altaffiltext{3}{Delaware Asteroseismic Research Center, Mt. Cuba Observatory,
Greenville, DE 19807}
\altaffiltext{4}{Department of Astronomy, University of Texas, Austin, TX 78712;
mikemon@rocky.as.utexas.edu}
\altaffiltext{5}{Meyer Observatory and Central Texas Astronomical Society, 209
Paintbrush, Waco, TX 76705; chandler@vvm.com}
\altaffiltext{7}{Korea Astronomy and Space Science Institute, Daejeon 34055, Korea}
\altaffiltext{8}{National Astronomical Observatories, Academy of Sciences, Beijing 10012, People's Republic of
China; xjjiang@bao.ac.cn}
\altaffiltext{9}{Fesenkov Astrophysical Institute, Almaty 050020, Kazakhstan}
\altaffiltext{10}{Ukrainian National Academy of Sciences, International Center for Astronomical,
Medical and Ecological Research, 27, Akademika Zabolotnoho Ave., 03680 Kyiv, Ukraine; sergeev@terskol.com }
\altaffiltext{11}{Russian Academy of Sciences, Institute of Astronomy, Terskol Branch, 81, Elbrus Ave., ap. 33, Tyrnyauz,
Kabardino-Balkaria Republic, 361623, Russian Federation; sergeev@terskol.com}
\altaffiltext{12}{Institute of Theoretical Physics and Astronomy, Vilnius
University, Vilnius, Lithuania; jr@itpa.lt}
\altaffiltext{13}{Ulupinar Observatory, \c Canakkale Onsekiz Mart University, Turkey}
\altaffiltext{14}{Astronomical Observatory of the Jagiellonian University, ul. Orla
171, 30-244 Cracow, Poland; szola@oa.uj.edu.pl}
\altaffiltext{15}{Mount Suhora Observatory, Cracow Pedagogical University, Ul.
Podchorazych 2, 30-084 Krakow, Poland; zola@astro1.as.ap.krakow.pl}
\altaffiltext{16}{Institut f\H ur Astrophysik, Universit\H at Wien, T\H urkenschanzstrasse 17, 1180 Wien, Austria}
\altaffiltext{17}{Institut fuer Astronomie und Astrophysik, Kepler Center for Astro and Particle Physics,
Eberhard Karls Universitaet Tuebingen, Sand 1, 72076 Tuebingen Germany; nagel@astro.uni-tuebingen.de}
\altaffiltext{18}{Konkoly Observatory, MTA CSFK, Konkoly Thege M. u. 15-17, H-1121 Budapest, Hungary}

@@

\begin{abstract}
We report on the analysis of 34 years of photometric observations of the pulsating
helium atmosphere white dwarf GD358.  The complete data set includes archival data from 1982-2006, 
and 1195.2 hours of new observations from 2007-2016. From this data set, we extract 15 frequencies 
representing g-mode pulsation modes, adding 4 modes to the 11 modes 
known previously. We present evidence that these 15 modes are $\ell=1$ modes, 13 of which belong to 
a consecutive sequence in radial overtone
$k$. We perform a detailed asteroseismic analysis using models that include parameterized, complex carbon and oxygen 
core composition profiles to fit the periods. Recent spectroscopic analyses place GD358 near the red edge of the DBV instability strip, at 24,000 $\pm$ 500~K and a \logg of 7.8 $\pm$ 0.08 dex. The surface gravity translates to a mass range of 0.455 to 0.540 \msun. Our best fit model has a temperature of 23,650~K and a mass of 0.5706 \msun ~. That is slightly more massive than what the most recent spectroscopy suggests. We find a pure helium layer mass of $10^{-5.50}$, consistent with the outward diffusion of helium over time.

@@

The subject of this paper, GD358 (V777 Her) is the brightest ($m_{\rm v}=13.7$) and best 
studied helium atmosphere white dwarf pulsator. It is located near the red edge of the 
instability strip, with a spectroscopic temperature of \teff\ $=24000\pm500$ ~K and \logg\ $=7.8$ 
\citep{Nitta12, Koester2013}. GD358's pulsation spectrum contains a series of independent 
radial overtones, many with complex frequency structure.  For one epoch of data taken during a WET run, models involving magnetic fields and oblique rotation have been proposed to explain such structure \citep{Montgomery10}.

@@

GD358 was discovered in 1982 \citep{Winget82} and has been the target of the Whole 
Earth Telescope (WET) in 1990, 1994, 2000, and 2006 \citep{Provencal09, Kepler03,Winget94}. 
New observations presented here include 278 individual observing runs (1105.1 hrs) spanning 
2007-2016 (Table \ref{journal}). Each season of observations was obtained as part of 
multi-site WET campaigns \citep{wet90}.

@@

\begin{figure}
\epsscale{0.7}
\plotone{terskol}
\caption{Light curve of GD358 obtained with the Peak Terksol 2.0 m telescope.  Each point corresponds 
to a 10 s exposure. The nonlinear, multiperiodic nature of this star is clearly evident.
(A color version of this figure is available in the online journal.)
\label{tersk}
}
\end{figure}

The complexities associated with GD358's pulsations (see Section \ref{freq}) led us to also 
re-reduce all available archival data \citep{Provencal09, Bradley04, Kepler03, Winget94, Winget82} to
insure continuity in methodology. The final result is a series of light curves 
for each observing season between 1982 and 2016. 
For the new observations, 2007 contains 8.1 hrs of observation, 2008 26.1 hrs, 2009 45 hrs, 
2010 201.3 hrs, 2011 401.1 hrs, 2012 150.5 hrs, 2013 87 hrs, 2014 184.6 hrs, 2015 55 hrs and 2016 90.6 hrs. 
Our coverage is not complete, and this incompleteness produces spectral leakage in the 
amplitude spectra. To quantify this, we sampled single sinusoids using exactly the 
same times as the original data for each season. The resulting amplitude spectrum, 
or ``spectral window'', is the pattern produced in the FT by a single frequency. 
The FTs for 2010, 2011, and 2014 are given in Fig.~\ref{fts}.

@@

We use {\sl Period04} \citep{Lenz05} for Fourier analysis and nonlinear least squares fitting to 
select statistically significant peaks in each FT. We adopt the criterion that a peak must have 
an amplitude at least four times greater than the average noise level in the given frequency range 
\citep{Provencal12}. We define ``noise'' as the frequency-dependent 
average amplitude after removal of the dominant frequencies. This is a conservative estimate, 
as it is impossible to ensure that all of the ``real'' frequencies are removed when determining
the noise level. This is certainly true for GD358, where the peaks above $\approx$ 2500 $\mu$Hz\ 
are combination frequencies (see Section \ref{mode}, \citet{Provencal09}).  Fig.~\ref{noise} displays the average noise 
as a function of frequency for the 2007-2016 observing seasons. A similar plot for the 
archival data is presented in Fig. 3 of \citet{Provencal09}. To confirm our uncertainty 
estimates, we calculated Monte Carlo simulations using the routine provided in {\sl Period04}.  
This routine generates a set of light curves using the original times, the fitted frequencies and 
amplitudes, and added Gaussian noise. A least squares fit is performed on each simulated light 
curve, with the distribution of fit parameters giving the uncertainties. Our Monte Carlo results 
are consistent with our average noise estimates.

\begin{figure}
\plotone{noise}
\caption{A comparison of the average noise as a function of frequency for the 2007-2016 observing 
seasons.  Each data set was prewhitened by its dominant frequencies.  The noise levels for each 
season are somewhat different.  This must be taken into account during frequency analysis.  
\label{noise}
}
\end{figure}

Having established our baseline noise levels, we proceed to frequency selection and identification.
Our frequency selection procedure involves identifying the largest amplitude resolved peak in the FT,
fitting a sinusoid at that frequency to the data set, subtracting the fit from the light curve, 
recomputing the FT, examining the residuals, and repeating the process until no significant power 
remains. This technique, known as prewhitening, must be employed with an over-abundance of caution, 
especially since we are aware of amplitude and/or frequency modulation in our data set. A detailed
discussion of the prewhitening procedure and steps taken to minimize the effects of amplitude 
modulation is given in \citet{Provencal09}. Our final identifications of independent frequencies
detected in each observing season are given in Table \ref{freq1} and Table \ref{freq2}.

@@

\subsection{Frequency Distribution}
Perusal of Tables \ref{freq1} and \ref{freq2} shows that GD358's observed frequencies vary in two
important ways.  First, frequencies detected in a given observing season are not found 
in all observing seasons. Asteroseismology is based on the assumption that the available pulsation
frequencies are linked to stellar structure.  Since we are fairly certain that GD358's internal structure 
does not change on the timescales of the observations, we can assume that GD358 excites 
different subsets of its available pulsations at different times. While this is a common phenomenon
seen in white dwarf pulsators, the selection mechanism remains unknown. The best way to 
determine GD358's complete set of pulsation frequencies is to combine frequency identifications 
from multiple observing seasons as outlined in \citet{Kleinman98}.

\begin{figure}
\epsscale{0.9}
%\plottwo{gd358multif_2015.eps}{gd358multi.eps}
%\centering{
%\includegraphics[width=1.0]{gd358multif_2015.eps}
%}
\plotone{gd358multif_2015.eps}
\caption{A schematic representation of GD358's pulsation modes for all available data between
1982 and 2015. Systematic patterns of distribution are evident. The bands between 2400 and 1000
\muHz\ (400 and 1000 s) are of particular importance for this work. (A color version of this 
figure is available in the online journal.)
\label{schematic}
}
\end{figure}

Fig.~\ref{schematic} presents a schematic representation of GD358's 
independent frequencies detected between 1982 and 2016.  
The features of asteroseismic importance are the localized bands between 900 and 2400
\muHz\ (1100 and 400 s). We interpret the bands to represent a series of modes of radial overtone $k$. The bands
themselves illustrate the second way in which GD358's frequencies vary. Each band consists of 
frequency detections from multiple observing seasons, but each band is significantly wider in 
frequency space than the frequency error of any single measurement, arguing that some process 
is acting on the frequencies. The simplest explanation is rotational splitting.  However, with the 
exception of the two highest frequency (shortest period) bands ($k=8$ and $k=9$ 
from \citet{Provencal09}), we find no clear evidence of stable multiplet structure in the frequency 
distributions of the lower frequency (longer period) bands (Fig.~\ref{rot}). This does not imply that the 
structures found by \cite{Winget94}, \cite{Kepler03}, \cite{Montgomery10} and others are not real. In 
particular, it is clear that the $k=12$ mode can be explained by the oblique rotation model during 2006. However, 
previous work represents short snapshots of GD358. When examined over timescales of decades, these structures 
do not regularly recur, and so cannot be interpreted as simple rotational splitting. The lower frequency band widths 
are most likely the result of various processes producing amplitude and/or frequency modulation that obscures any 
underlying signatures of rotational splitting. 
\begin{figure}
 \epsscale{1.0}
 \plotone{gd358k17_k8.eps}
% \plottwo{gd358multifk17.eps}{gd358multifk8.eps}
 \caption{The detailed schematic distribution of frequencies for the bands near 1300({\em{right}}
 and 2360 \muHz\ ({\em{left}}). As an example of the higher frequency bands, the 1300 \muHz\ band 
 shows no multiplet structure, unlike the 2360 \muHz\ band. Here we see clear evidence of multiplet 
 structure. Assuming the triplet represents
 $\ell=1$, this implies a rotation period of $\approx 1.5$ days. Note changes in the x scale for both axes.
 (A color version of this figure is available in the online journal.)
 \label{rot}}
\end{figure}

Fig. \ref{schematic} also shows that the widths of the bands are not constant, but change 
from band to band. \citet{Bell15} presents an interesting analysis of the hydrogen atmosphere pulsator 
(DAV) KIC4552982, in which they identify 17 bands of pulsation frequencies. KIC4552982 is one of the 
coolest ZZ Cetis known \citep{Tremblay2013}, and it follows the general pattern exhibited 
by GD358: the highest frequency (shortest period) mode shows evidence of rotational splitting, while the 
lower frequency (longer period) modes are complex bands. The authors note that this DAV's bands have 
different widths in frequency space, and that there may be astronomical significance to this. 
Although the observational timebases and coverage are quite different (20 continuous months 
for KIC4552982 vs 34 incomplete years for GD358), our data presents the opportunity to investigate this 
for a cooler DB pulsator.  We measured the widths of each of GD358's band where we have
more than 10 detections. We define ''width'' as the difference between the lowest and highest frequency 
detected in each band. Fig. \ref{thick} presents the results. We find no correlation of width with number
of detected peaks in each band. Interestingly, the widths of GD358's bands are commensurate with those 
found in KIC4552982. We find a general increase in width with decreasing frequency (increasing period), 
until we reach the band at 1238 \muHz\ (807 s). This band has a width at least twice as wide as any other.

\citet{Mont2016} recently outlined a possible explanation for the behavior seen in the low frequency modes
of these cool DAVs that should also apply to GD358. White dwarfs pulsate in nonradial g-modes. As a DBV such as 
GD358 pulsates, it experiences local surface temperature variations as large as 3000 K.  The temperature 
variation affects different modes in different ways.  An appropriate analogy is to consider each mode's 
propagation region as a box with a lid. The box is defined as the region where the mode frequency is 
less than both the buoyancy (Brunt-V{\"a}is{\"a}l{\"a}) and acoustic (Lamb) frequencies.  The box's lid 
represents the mode's outer turning point. For short period modes (such as $k=8$ and $k=9$ in GD358), the 
lid is defined by the acoustic frequency, which is relatively insensitive to surface temperature variations. 
As the star pulsates, the box will not change, so these modes should be stable.  For the longer period modes, 
the lid of the box is defined by the buoyancy frequency, which goes to zero at the base of the surface 
convection zone. This is the important point: for longer period modes, the box lid
is actually defined by the base of the convection zone, which is very sensitive to local temperature variations.  
As GD358 pulsates, its convection zone deepens and thins in response to the local temperature variations. 
In our analogy, the lid of the box moves, effectively changing the characteristics of the box. Long period modes with 
outer turning points defined by the base of the convection zone should be perturbed and this is indeed 
what we see in GD358.

An additional interesting behavior is given by the distribution of average amplitudes for the bands 
(Fig~\ref{schematic}). In particular, the two bands at 1857.7 and 2007.6  \muHz\ have never been observed 
at amplitudes above 4 mma. The band at 1369 \muHz\ is also only observed at lower amplitudes. Interestingly, 
the band at 1741.5 \muHz\ was not observed at large amplitude prior to 2006, and it has remained at high 
amplitude since that time.

To summarize this section in broad brush strokes, the observed global pulsations involve the whole star, 
but each pulsation samples the star in slightly different ways.  Modes with lower frequencies 
(higher radial $k$ values) preferentially sample the outer layers, while modes with higher frequencies 
(lower radial $k$ values) have outer turning points that are farther from the surface, and so sample the 
deeper interior. It makes intuitive sense that lower frequency modes would be affected by processes 
confined to the outer stellar atmosphere, such as the convection zone. We speculate that the 
observed band widths and pulsation amplitudes contain information about the convection zone and/or any surface
magnetic field. Further investigation requires guidance from theory.

@@

\subsection{Mode Identification}\label{mode}
Our current work has produced a well defined sequence of modes, adding to 
previous studies \citep{Montgomery10, Provencal09, Metcalfe00, Winget94}. The previous 
identification of these modes as a series of $l$=1 radial overtones is based mostly on 
the pulsation frequency distribution and limited spectroscopic analysis 
\citep{Kotak02, Castanheira05}. It is important to further investigate these identifications 
as we initiate an in depth asteroseismic investigation.

@@

Finally, given the $l$=1 identification and the lack of definitive multiplet structure for the lower 
frequency modes, the best way to determine the central frequency for each band is simply to 
average the detected frequencies in the bands.  We experimented with numerous weighting techniques, 
and determined there is no significant difference in our solutions.  Our final frequencies for each band 
are given in Table~\ref{gd}. We use these periods in our asteroseismic fitting.

@@

To compute our models, we used the White Dwarf Evolution Code (WDEC). The WDEC uses hot  and self-consistently allows them to relax to be solutions of the equations of stellar structure with the temperature of our choice.
polytrope models with temperatures above 100{,}000~K as starting model and numerically evolves them until they are thermally relaxed 
solutions to the stellar structure equations and have the temperature of our choice. The mass is also fixed as an input, and so is the internal chemical composition profiles (no mass loss, no time dependent diffusion of elements). Each model we compute for our grids is the result 
of such an evolutionary sequence. The WDEC is described in detail in \citet{Lamb75} and 
\citet{Wood90}. We used smoother core composition profiles and implemented more complex profiles 
that result from stellar evolution calculations \citep{Salaris97}. We updated the envelope 
equation of state tables from those calculated by \citet{Fontaine77} to those given by 
\citet{Saumon95}. We use OPAL opacities \citep{Iglesias96} and plasmon neutrino rates 
published by \citet{Itoh96}.

@@

Before we refine the period-by-period fitting optimization, it is worthwhile to step back and consider 
what we can learn from the average period spacing of GD358. The average period spacing provides an 
asteroseismic measure of the mass and temperature of the star, independent of the details of 
internal chemical composition profiles. Higher $k$ modes are not strongly trapped in the core and 
according to asymptotic theory, they should be nearly evenly spaced in period. This spacing is 
given by \citet{Unno89}.
